---
pagetitle: "tesselle: R Packages & Archaeology"
resources: 
  - "sitemapindex.xml"
  - "packages.json"
listing:
  - id: gallery
    template: gallery.ejs
    contents: gallery.yml
    sort-ui: false
    filter-ui: true
---

```{r}
#| label: packages 
#| echo: false
## Get packages info
repo <- utils::contrib.url("https://tesselle.r-universe.dev")
pkg <- utils::available.packages(contriburl = repo)
pkg <- as.data.frame(pkg)
url_pkg <- sprintf("https://packages.tesselle.org/%s", pkg$Package)
```

```{r}
#| label: sitemap 
#| echo: false
## Build sitemap index
loc <- paste0(url_pkg, "/sitemap.xml")
map <- sprintf("  <sitemap>\n    <loc>%s</loc>\n  </sitemap>", loc)
cat(
  '<?xml version="1.0" encoding="UTF-8"?>',
  '<sitemapindex xmlns="http://www.sitemaps.org/schemas/sitemap/0.9">',
  '  <sitemap>',
  '    <loc>https://packages.tesselle.org/sitemap.xml</loc>',
  '  </sitemap>',
  map,
  '</sitemapindex>',
  file = "sitemapindex.xml",
  sep = "\n",
  append = FALSE
)
```

```{r}
#| label: search 
#| echo: false
## Build search index
search_pkg <- list()
for (i in seq_along(url_pkg)) {
  path <- url_pkg[[i]]
  tmp <- try(
    expr = rjson::fromJSON(file = paste0(path, "/search.json")), 
    silent = TRUE
  )
  if (!inherits(tmp, "try-error")) {
    for (j in seq_along(tmp)) {
      ## Add package name
      tmp[[j]]$package <- pkg$Package[[i]]
    }
    search_pkg <- c(search_pkg, tmp)
  }
}
cat(rjson::toJSON(search_pkg), file = "packages.json", append = FALSE)
```

::: {#hero-banner .column-screen}
::: {.grid .column-page}
::: {.headline .g-col-lg-6 .g-col-12 .g-col-md-12}
# Welcome
[**tesselle**](https://packages.tesselle.org) is a collection of [R](https://www.r-project.org/) packages for research and teaching in archaeology. These packages focus on quantitative analysis methods developed for archaeology. The **tesselle** packages are designed to work seamlessly together and to complement general-purpose and other specialized statistical packages.
:::

::: {.g-col-lg-6 .g-col-12 .g-col-md-12}
# Read the doc

Quickly discover relevant content by searching the documentation or exploring the [project bibliography](https://www.zotero.org/groups/2894473/tesselle/library).

<form role="search">
<div class="form-group">
<label for="search-packages"><strong>Search in the documentation</strong></label>
<input type="search" class="form-control" aria-label="Search" name="search-packages" data-search-index="/packages.json" id="search-packages" placeholder="e.g. seriation" autocomplete="off">
</div>
</form>
:::

:::
:::

::: {.column-page}
# Packages

::: {#gallery}
:::

:::
