---
title: "tesselle"
---

This is a repository holding R packages of the [tesselle](https://www.tesselle.org/) project. Most of the packages are distributed on [CRAN](https://cran.r-project.org/), but some data packages are too large and can only be installed from this repository.

If available, CRAN releases must be regarded as the preferred source.

## Download tesselle packages

If you want to install a package, simply use `install.packages()` with the additional repository:

```{r, eval=FALSE}
repos <- c("https://packages.tesselle.org", getOption("repos"))
install.packages("tabula", repos = repos, type = "source")
```

## Use the repository

You can use this repository in your R package (always prefer the CRAN release if available). To do so, prepare the `DESCRIPTION` file of your R package:

* List the package under `Suggests:`
* Add the line `Additional_repositories: https://packages.tesselle.org`
* Test your package with `R CMD check --as-cran`

## Packages

```{r, echo=FALSE}
repo <- utils::contrib.url("https://packages.tesselle.org")
pkg <- utils::available.packages(contriburl = repo)

info <- as.data.frame(pkg[, c("Package", "Version", "Depends", "License")])
info$Package <- sprintf("<a href=\"https://packages.tesselle.org/%s\" title=\"Read the doc\">%s</a>", 
                        info$Package, info$Package)
rownames(info) <- NULL

knitr::kable(info, escape = FALSE)
```
